quollr: An R Package for Visualizing 2-D Models from Nonlinear Dimension Reductions in High-Dimensional Space

### 2025-12-08 paper-quollr.Rmd
Fixed the Figure 3

algofig <- bscols(
  htmltools::div(
    style = "
      display: flex;
      justify-content: center;     /* centers the grid horizontally */
      align-items: center;          /* optional: centers vertically if space allows */
      margin: 0 auto;
      padding: 0;
    ",
    htmltools::div(
      style = "
        display: grid;
        grid-template-columns: 1fr 1fr;
        gap: 0px;
        align-items: start;
        justify-items: center;
        margin: 0;
        padding: 0;
      ",
      htmltools::div(style = 'margin: 0; padding: 0;  height: 300px; width: 225px;', hex_grid_poly_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 350px; width: 400px;', hex_centroids_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 280px; width: 225px;', wireframe_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; margin-left: 60px; height: 300px;', scurve_umap_model_vis_n)
    )
  ),
  device = "xs"
)

@@

linked_plt_best <- crosstalk::bscols(
  htmltools::div(style="display: grid; grid-template-columns: 1fr 1fr;",
                 nldr_plt,
                 htmltools::div(style = "margin-top: 20px;", langevitour_output)
  ),
  device = "xs"
)
```

>>>>

algofig <- bscols(
  htmltools::div(
    style = "
      display: flex;
      justify-content: center;     /* centers the grid horizontally */
      align-items: center;          /* optional: centers vertically if space allows */
      margin: 0 auto;
      padding: 0;
    ",
    htmltools::div(
      style = "
        display: grid;
        grid-template-columns: 1fr 1fr;
        gap: 0px;
        align-items: start;
        justify-items: center;
        margin: 0;
        padding: 0;
      ",
      htmltools::div(style = 'margin: 0; padding: 0;  height: 300px; width: 300px;', hex_grid_poly_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 350px; width: 400px;', hex_centroids_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; height: 300px; width: 300px;', wireframe_scurve_int),
      htmltools::div(style = 'margin: 0; padding: 0; margin-left: 60px; height: 300px;', scurve_umap_model_vis_n)
    )
  ),
  device = "xs"
)

@@

nldr_plt <- ggplotly(nldr_plt, width = 300,
                     height = 300, tooltip = "none") |>
  style(unselected=list(marker=list(opacity=1))) |>
  highlight(on="plotly_selected", off="plotly_deselect") |>
  config(displayModeBar = FALSE)

langevitour_output <- langevitour::langevitour(point_data[1:num_highd_col],
                                               lineFrom = edge_data$from_reindexed,
                                               lineTo = edge_data$to_reindexed,
                                               group = factor(point_data$type,
                                                              c("0", "1", "2", "3", "4", "5", "6", "model")),
                                               pointSize = append(rep(point_sizes[1], NROW(df_b)),
                                                                  rep(point_sizes[2], NROW(df))),
                                               levelColors = c('#66c2a5','#fc8d62','#8da0cb','#e78ac3','#a6d854','#ffd92f','#e5c494', "#000000"),
                                               link=shared_df,
                                               linkFilter=FALSE,
                                               width = "200px", height = "100px")

linked_plt_best <- crosstalk::bscols(
    htmltools::div(
        style = "display: grid; grid-template-columns: 1fr 1fr;
    gap: 0px;
    align-items: center;
    justify-items: center;
    margin: 0;
    padding: 0;",
        nldr_plt, langevitour_output
    ),
    device = "xs"
)
```
